---
title: "CTTIR packages & repositories"
---

Public repositories in the [CTTIR](https://github.com/CTTIR) GitHub organisation,
reviewed on **23 September 2026**. The inventory contains **38 public repositories**.
Tables are rendered from `_data/cttir-repos.json`, refreshed by
`scripts/fetch-cttir-repos.R` and validated in CI.

`cellspecR` and `gatekeepR` are 1.0.0 release candidates; `bloodspottR` is
experimental; `brainwritR` is a development R/Shiny application. The current
`shinylaunchR` 0.2.0-rc.1 candidate is unpublished, following its 0.1.0 GitHub
release. `qupflowR` and `cttir.r-universe.dev` are currently empty placeholders.
See the [organisation profile](https://github.com/CTTIR) for the curated overview.

## R repositories

GitHub's primary-language classification is used here; it includes R applications
and does not establish package maturity or CRAN availability.

```{r}
#| label: cttir-packages-table
#| echo: false
#| message: false
#| warning: false

repos <- jsonlite::read_json("../_data/cttir-repos.json", simplifyVector = FALSE)

# Filter: keep R packages only. Excludes the meta/non-package repos.
exclude <- c("ressources", "website", ".github", "pwa-quest", "courses", "tutorials")
pkgs <- Filter(function(r) {
  identical(r$language, "R") && !(r$name %in% exclude) &&
    isFALSE(r$archived) && isFALSE(r$fork)
}, repos)

# Sort alphabetically for stable output
pkgs <- pkgs[order(vapply(pkgs, function(r) r$name, character(1)))]

format_license <- function(r) {
  if (is.null(r$license) || is.null(r$license$spdx_id) ||
      identical(r$license$spdx_id, "NOASSERTION")) {
    "—"
  } else {
    r$license$spdx_id
  }
}

format_homepage <- function(r) {
  if (is.null(r$homepage) || !nzchar(r$homepage)) {
    "—"
  } else {
    sprintf("[site](%s)", r$homepage)
  }
}

format_desc <- function(r) {
  if (is.null(r$description) || !nzchar(r$description)) "—" else r$description
}

df <- data.frame(
  Package    = vapply(pkgs, function(r) sprintf("[`%s`](%s)", r$name, r$html_url), character(1)),
  Description = vapply(pkgs, format_desc, character(1)),
  License    = vapply(pkgs, format_license, character(1)),
  Site       = vapply(pkgs, format_homepage, character(1)),
  stringsAsFactors = FALSE,
  check.names = FALSE
)

knitr::kable(df, format = "markdown")
```

## Other repositories

```{r}
#| label: cttir-other-repositories
#| echo: false
other <- Filter(function(r) !(r$name %in% vapply(pkgs, function(p) p$name, character(1))), repos)
other <- other[order(vapply(other, function(r) r$name, character(1)))]
knitr::kable(data.frame(
  Repository = vapply(other, function(r) sprintf("[`%s`](%s)", r$name, r$html_url), character(1)),
  Description = vapply(other, format_desc, character(1)),
  check.names = FALSE
), format = "markdown")
```

## Notes

- License `—` means GitHub's licence detector did not find an SPDX-identified `LICENSE` file in the repository's expected location. This is editorial debt to resolve in each package.
- Description `—` means the GitHub repository description field is blank.
- The list is generated at build time. To refresh the underlying inventory, run `Rscript scripts/fetch-cttir-repos.R` and commit the updated `_data/cttir-repos.json`.
